Boundary condition changing operators and singular vectors of Virasoro and affine Lie algebra modules

### 2013-02-08 AffineLieAlgebras/Simons/talk.tex
Minor changes

\documentclass[a4paper]{article}
The title is
``Boundary condition changing operators and singular vectors Virasoro and
affine Lie algebra modules''.

Abstract:
We consider the behaviour of CFT correlation functions with respect to
Schramm-Loewner evolution with additional Brownian motion on gauge
group. Using the analogy with lattice models we consider
correlation functions that satisfy martingale conditions and contain
boundary condition changing operators and primary fields.
Martingale conditions can be rewritten as algebraic relations on
boundary condition changing operators and interpreted from
representation-theoretic point of view.

\begin{document}
Hello!
It's a great pleasure for me to be here in Simons Center for geometry and physics. 
My talk is called 
\end{document}

>>>>

\documentclass[a4paper]{article}

\title{Boundary condition changing operators and singular vectors of Virasoro and
affine Lie algebra modules}

\author{Anton Nazarov}
\begin{document}
\maketitle
\begin{abstract}
We consider the behaviour of CFT correlation functions with respect to
Schramm-Loewner evolution with additional Brownian motion on gauge
group. Using the analogy with lattice models we consider
correlation functions that satisfy martingale conditions and contain
boundary condition changing operators and primary fields.
Martingale conditions can be rewritten as algebraic relations on
boundary condition changing operators and interpreted from
representation-theoretic point of view.
\end{abstract}

Hello!
It's a great pleasure for me to be here in Simons Center for geometry and physics. 
My talk is called ``Boundary condition changing operators and singular vectors of Virasoro and
affine Lie algebra modules''. 
\end{document}
